---
title: "Vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


### Installation

```{r setup}
# devtools::install_github("samuelreuther/SRxgboost")
library(SRxgboost)
```


### TODOs

- SRxgboost_run:  
  - Fehler bei test-02_SRxgboost_run:  
    - mclass_no_folds_softprob  
    - mclass_no_folds_softprob_wprec  
    - mclass_no_folds_softmax  
  - remove parameters for Feature Selection:  
    - feat_sel  
    - Feat_Sel  
    - Feat_Sel_Vars  
    - Selected_Features = FALSE  
  - add columns in summaryCV for:  
    - train1f/test1f  
    - train/CV  
    - trainfinal/testfinal (calculate test-results if y_test is provided)  
    - fixed metrics AUC/accuracy/R2/RMSE/MAPE  
  - plot shapley contribution: more expressive graphic for multilabel classification  
  - Shap values für XGBOOST-Modelle: Funktion um für Testdata zu kalkulieren  
- latin hypercube sampling of hyper-parameter:  
  - https://statcompute.wordpress.com/2019/07/06/latin-hypercube-sampling-in-hyper-parameter-optimization/  
  - Enforcing Monotonic Constraints:  
    - https://xgboost.readthedocs.io/en/latest/tutorials/monotonic.html  
    - params_constrained = params.copy()  
    - params_constrained['monotone_constraints'] = "(1,-1)"  
    - (1,-1,0): increasing/decreasing constraint, no constraint on the third  
    - model_with_constraints = xgb.train(params_constrained, d_train,  
                                         num_boost_round = 1000, evals = evallist)  
- SRxgboost_prepare_data:  
  - Factor Encoder OOF hinzufügen:  
    - http://docs.h2o.ai/h2o/latest-stable/h2o-docs/data-munging/target-encoding.html  
    - https://towardsdatascience.com/getting-deeper-into-categorical-encodings-for-machine-learning-2312acd347c8  
- SRxgboost_select_variables:  
  - generate 3 random variables per category  
  - take mean of random variable per category as threshold per variable category  
- Beispiel für "Starter-Code für Machine Learning-Modell mit XGBOOST inkl. Modell Explainability" erstellen  
- Surrogate Model berechnen

