---
title: "Vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


### Installation

```{r setup}
# devtools::install_github("samuelreuther/SRxgboost")
library(SRxgboost)
```


### TODOs

- SRxgboost_run:  
  - remove parameters for Feature Selection: 
    - feat_sel
    - Feat_Sel
    - Feat_Sel_Vars
    - Selected_Features = FALSE
  - add columns in summaryCV for:  
    - train1f/test1f  
    - train/CV  
    - trainfinal/testfinal (calculate test-results if y_test is provided)  
    - fixed metrics AUC/accuracy/R2/RMSE/MAPE  
  - plot shapley contribution: more expressive graphic for multilabel classification  
- latin hypercube sampling of hyper-parameter:  
  - https://statcompute.wordpress.com/2019/07/06/latin-hypercube-sampling-in-hyper-parameter-optimization/
  - Enforcing Monotonic Constraints:  
    - https://xgboost.readthedocs.io/en/latest/tutorials/monotonic.html  
    - params_constrained = params.copy()  
    - params_constrained['monotone_constraints'] = "(1,-1)"  
    - (1,-1,0): increasing/decreasing constraint, no constraint on the third  
    - model_with_constraints = xgb.train(params_constrained, d_train,  
                                         num_boost_round = 1000, evals = evallist)  
  
  
